---
title: "12.6.1"
author: "Han Nguyen"
date: "February 25, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(tidyr)
who

who1 <- who %>% 
  gather(new_sp_m014:newrel_f65, key = "key", value = "cases", na.rm = TRUE)
who1

who1 %>% 
  count(key)

who2 <- who1 %>% 
  mutate(key = stringr::str_replace(key, "newrel", "new_rel"))
who2

who3 <- who2 %>% 
  separate(key, c("new", "type", "sexage"), sep = "_")
who3

who3 %>% 
  count(new)

who4 <- who3 %>% 
  select(-new, -iso2, -iso3)

who5 <- who4 %>% 
  separate(sexage, c("sex", "age"), sep = 1)
who5
```

#### Question 3
I claimed that \texttt{iso2} and \texttt{iso3} were redundant with \texttt{country}. Confirm this claim.

```{r}
select(who3, country, iso2, iso3) %>%
  distinct() %>%
  group_by(country) %>%
  filter(n() > 1)
```
Since this returns 0 distinct tibbles and groups, it shows that iso2 and iso3 are redundant with country.


#### Question 4
For each country, year, and sex compute the total number of cases of TB. Make an informative visualisation of the data.

```{r}
who5 %>%
  group_by(country, year, sex) %>%
  filter(year > 1995) %>%
  summarise(cases = sum(cases)) %>%
  unite(country_sex, country, sex, remove = FALSE) %>%
  ggplot(aes(x = year, y = cases, group = country_sex, colour = sex)) +
  geom_line()
```
Countries were combined with sex because there were so many countries that a ggplot would not represent each one well. 